ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-10-04 rebuttal.tex

\begin{reviewer}
    %
    16.~The Python package Cerberus is used to validate the format and content of the given ChemKED
    file. How does this package handles/reports the inconsistencies with the schemas? As far as my
    local test went with giving a corrupted YAML file to the ChemKED initiator, the package just
    spits out a Python error, which might be not the most user-friendly solution.
    %
\end{reviewer}

\begin{response}
    %
    We recognize that this is a limitation of the current version of PyKED. The technical reason for
    this in the Cerberus package has very recently been resolved (see
    \url{https://github.com/pyeve/cerberus/issues/278}), so we plan to update the error reporting
    mechanism in PyKED to report well-formatted errors that have a detailed description of the
    error. We have opened a public issue to track the progress on this:
    \url{https://github.com/pr-omethe-us/PyKED/issues/78}. Thank you for suggesting this
    improvement.
    %
\end{response}

\begin{reviewer}
    %
    17.~A recurring issue with actively developing codes is backwards compatibility. How are the
    authors planning on addressing this issue?
    %
\end{reviewer}

\begin{response}
    %
    We agree with the reviewer that backwards compatibility may become an issue. We have addressed
    this concern in ChemKED by including the database version as one of the required keys in the
    ChemKED file. Although the functionality doesn't exist yet, we intend to be able to check this
    version and report any feature deprecation or removal to the user (see
    \url{https://github.com/pr-omethe-us/PyKED/issues/22}), and we plan to provide an automated
    upgrade path for ChemKED files when backwards-incompatible changes are made. In addition, we use
    the widely supported Semantic Versioning paradigm, where changes in the various parts of the
    version number (vX.Y.Z) have specific meaning; changing the major version (X) indicates a
    backwards incompatible change, changing the minor version (Y) indicates a backwards compatible,
    but somewhat large, change, and changing the patch version (Z) indicates a bug fix with no
    anticipated incompatibilities.

### 2017-10-07 pyked.tex
Fix common-properties YAML demo
add explanation of "open" for #6

@@

Frequently, experimental series hold certain properties constant, such as initial mixture
composition or pressure, and use the same method to detect ignition delay. \ck{} files support a
\yabox|common-properties| convenience section where these common details may be defined once, and
referenced in each element of the \yabox|datapoints| sequence. This block uses the ability of YAML
files to define an anchor with the \yabox|&| symbol and refer to that section later with the
\yabox|*| symbol:
%
\begin{yamlbox}
common-properties:
  composition: &comp
    kind: mole fraction
    species:
      ...
  ignition-type: &ign
    ...
datapoints:
  composition: *comp
  ignition-type: *ign
  temperature: 1000 kelvin
  ...
\end{yamlbox}
%
The \yabox|common-properties| section is not required, but can save space and
help avoid errors when several data points share some common values. However, even if
properties are specified in the \yabox|common-properties| section, they must also be
explicitly specified and referenced in the \yabox|datapoints| section for each data point,
as seen in the previous code.

>>>>

%discuss open source definition here
(When we describe a software package or project as ``closed,'' we are generally
contrasting it with the open source definition~\cite{opensource}. In brief, to be
``open,'' a project must provide free and unrestricted access to source code and\slash
or data, allow free redistribution, permit derived works, and not discriminate against
any people or areas of work, along with a few other criteria.)

@@

Frequently, experimental series hold certain properties constant, such as initial mixture
composition or pressure, and use the same method to detect ignition delay. \ck{} files support a
\yabox|common-properties| convenience section where these common details may be defined once, and
referenced in each element of the \yabox|datapoints| sequence. This block uses the ability of YAML
files to define an anchor with the \yabox|&| symbol and refer to that section later with the
\yabox|*| symbol:
%
\begin{yamlbox}
common-properties:
  composition: &comp
    kind: mole fraction
    species:
      ...
  ignition-type: &ign
    ...
datapoints:
  - composition: *comp
    ignition-type: *ign
    temperature:
      - 1000 kelvin
  ...
\end{yamlbox}
%
The \yabox|common-properties| section is not required, but can save space and
help avoid errors when several data points share some common values. However, even if
properties are specified in the \yabox|common-properties| section, they must also be
explicitly specified and referenced in the \yabox|datapoints| section for each data point,
as seen in the previous code.
